GHRVis:

### 2022-01-23 paper/GHRVis.tex
feat: move all nodes and move back nodeX
feat: add a table for dorling papers
draft: related work
draft: related work: media
draft: data

% ---------------------------------------------------------------------------
% Author guideline and sample document for EG publication using LaTeX2e input
% D.Fellner, v1.15, Dec 14, 2018

@@

% !! *please* don't change anything above
% !! unless you REALLY know what you are doing
% ------------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage{dfadobe}

% \usepackage{cite}  % comment out for biblatex with backend=biber
% ---------------------------
\biberVersion
\BibtexOrBiblatex
\usepackage[backend=biber,bibstyle=EG,citestyle=alphabetic,backref=true]{biblatex}
%\addbibresource{egbibsample.bib}
% ---------------------------  
\electronicVersion
\PrintedOrElectronic
% for including postscript figures
% mind: package option 'draft' will replace PS figure by a filename within a frame
\ifpdf \usepackage[pdftex]{graphicx} \pdfcompresslevel=9
\else \usepackage[dvips]{graphicx} \fi

@@

\addbibresource{LetterVis.bib}

@@

@@

\usepackage{enumitem}

@@

% \author[Q. Wang \& R. S. Laramee]
% {\parbox{\textwidth}{\centering Q. Wang
%   and R. S. Laramee
%     }
%     \\
% \parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK}
% }

% \author[Q. Wang \& R. S. Laramee \& A. S. Lacey \& W. O. Pickrell]
% {\parbox{\textwidth}
%   {\centering Q. Wang$^{1}$, R. S. Laramee$^{1}$, A. Lacey$^{2,3}$ \& W. O. Pickrell$^{2,4}$}
%   \\
%   {\parbox{\textwidth}
%     {\centering $^1$School of Computer Science, University of Nottingham, UK\\
%         $^2$Neurology and Molecular Neuroscience Group, Institute of Life Science, Swansea University, UK\\
%         $^3$Population Data Science, Swansea University Medical School, Swansea University, UK\\
%         $^4$Neurology Department, Morriston Hospital, Swansea Bay University Healthboard, UK
%     }
%   }
% }

@@

\definecolor{Mycolor1}{HTML}{4C5866} %#4C5866
\definecolor{Mycolor2}{HTML}{A6B6D2} %#A6B6D2
\definecolor{Mycolor3}{HTML}{C1D4E8} %#C1D4E8
\definecolor{Mycolor4}{HTML}{F7F7FE} %#F7F7FE
\definecolor{Mycolor5}{HTML}{d8f3dc} %#d8f3dc
\definecolor{Mycolor6}{HTML}{EC6A5C} %#EC6A5C
\newcommand{\mycolorbox}[2]{\begingroup\setlength{\fboxsep}{2pt}\colorbox{#1}{#2}\endgroup}

@@

\section{Introduction and Motivation}

\section{Related Work}

\section{Data Description}

@@

>>>>

@@

% !! *please* don't change anything above
% !! unless you REALLY know what you are doing
% ------------------------------------------------------------------------

\usepackage[T1]{fontenc}
\usepackage{dfadobe}

% \usepackage{cite}  % comment out for biblatex with backend=biber
% ---------------------------
\biberVersion
\BibtexOrBiblatex
\usepackage[backend=biber,bibstyle=EG,citestyle=alphabetic,backref=true,url=false]{biblatex}
%\addbibresource{egbibsample.bib}

\renewbibmacro*{doi+eprint+url}{%
    \printfield{doi}%
    \newunit\newblock%
    \iftoggle{bbx:eprint}{%
        \usebibmacro{eprint}%
    }{}%
    \newunit\newblock%
    \iffieldundef{doi}{%
        \usebibmacro{url+urldate}}%
        {}%
    }

\addbibresource{GeoVis.bib}

\newcommand{\citetitlea}[1]{\citefield{#1}{title}}

% ---------------------------  
\electronicVersion
\PrintedOrElectronic
% for including postscript figures
% mind: package option 'draft' will replace PS figure by a filename within a frame
\ifpdf \usepackage[pdftex]{graphicx} \pdfcompresslevel=9
\else \usepackage[dvips]{graphicx} \fi

@@

@@

% code listing
\usepackage{listings}
\lstdefinestyle{customc}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},
  commentstyle=\itshape\color{purple!40!black},
  identifierstyle=\color{blue},
  stringstyle=\color{orange},
}

\lstdefinestyle{customasm}{
  belowcaptionskip=1\baselineskip,
  xleftmargin=\parindent,
  language=[x86masm]Assembler,
  basicstyle=\footnotesize\ttfamily,
  commentstyle=\itshape\color{purple!40!black},
}

\lstset{escapechar=@,style=customc}

@@

@@

\author[Q. Wang \& R. S. Laramee]
{\parbox{\textwidth}{\centering Q. Wang
  and R. S. Laramee
    }
    \\
\parbox{\textwidth}{\centering School of Computer Science, University of Nottingham, UK}
}

@@

\definecolor{Mycolor1}{HTML}{4C5866} %#4C5866
\definecolor{Mycolor2}{HTML}{A6B6D2} %#A6B6D2
\definecolor{Mycolor3}{HTML}{67daff} %#67daff
\definecolor{Mycolor4}{HTML}{F7F7FE} %#F7F7FE
\definecolor{Mycolor5}{HTML}{666ad1} %#666ad1
\definecolor{Mycolor6}{HTML}{ffbb93} %#ffbb93
\newcommand{\mycolorbox}[2]{\begingroup\setlength{\fboxsep}{2pt}\colorbox{#1}{#2}\endgroup}

% table cite
\newcommand{\citea}[1]{\citeauthor{#1}\cite{#1}}

% customized table headers
\newcommand{\theaderR}[1]{\multicolumn{1}{c|}{\cellcolor{Mycolor3} \textbf{\rotatebox{90}{#1 \phantom{-} }}}}
\newcommand{\theaderP}[1]{\cellcolor{Mycolor3} \textbf{#1}}

@@

\input{section/introduction}

\input{section/related}

\input{section/data}

@@

\subsection{VPSC}
